### 2023-02-13 chapters/appendix.tex
fvgm appendix

\appendix

\chapter{Feature Correlations in SSAT-based Fairness Verifier: {\justicia}}
\label{sec:CNF_feature_correlation}
In Chapter~\ref{chapter:justicia}, {\justicia} verifies the fairness of CNF classifiers without considering correlation among features. In this chapter, we address fairness verification of CNF classifiers with correlated features. In particular, we present the encoding of conditional probabilities from a Bayesian network into the SSAT formulation in {\justicia}.

@@

\paragraph{Quantifiers in $ \phi_{\widehat{Y}} \wedge \phi_\BN $.}
We now discuss the quantifiers in $ \phi_{\widehat{Y}} \wedge \phi_\BN $, the SSAT solution of which  constitutes the maximum (minimum) probability of positive prediction of a CNF classifier. $ \phi_{\widehat{Y}} \wedge \phi_\BN $ contains four  categories of variables : (i) sensitive variables $ \sensitive $, (ii) non-sensitive variables $ \nonsensitive $, (iii) indicator variables $  \lambda_{V_i} $, and (iv) auxiliary variables $ \lambda_{v,\mathbf{u}} $. Among them, (iii) and (iv) are associated with $ \phi_\BN $ and the rest for $ \phi_{\widehat{Y}} $. For computing the maximum probability of positive prediction of the classifier, we construct  an exists-random-exists (ERE) SSAT formula with following quantifiers: we set sensitive features $ \sensitive $ with existential quantifiers in the beginning of the prefix of the SSAT formula followed by $  \lambda_{V_i}, \lambda_{v,\mathbf{u}} $, and $ X_j \in \nonsensitive \setminus \mathbf{V} $ with randomized quantifiers. The remaining variables  $ X_i \in \mathbf{V} $ are existentially quantified as their assignment is fixed by indicator variables $ \lambda_{V_i} $. In contrast, for computing the minimum probability of positive prediction of the classifier, we consider an universal-random-exists (URE) SSAT formula  where we set sensitive features $ \sensitive $ as universal quantifiers with all other quantifiers remaining same.

>>>>

\chapter{Feature Correlations in SSAT-based Fairness Verifier}
%\label{chapter:CNF_feature_correlation}
In Chapter~\ref{chapter:justicia}, {\justicia} verifies the fairness of CNF classifiers without considering correlation among features. Now, we address fairness verification of CNF classifiers with correlated features. In particular, we present the encoding of conditional probabilities from a Bayesian network into the SSAT formulation in {\justicia}.

@@

\paragraph{Quantifiers in $ \phi_{\widehat{Y}} \wedge \phi_\BN $.}
We now discuss the quantifiers in $ \phi_{\widehat{Y}} \wedge \phi_\BN $, the SSAT solution of which  constitutes the maximum (minimum) probability of positive prediction of a CNF classifier. $ \phi_{\widehat{Y}} \wedge \phi_\BN $ contains four  categories of variables: (i) sensitive variables $ \sensitive $, (ii) non-sensitive variables $ \nonsensitive $, (iii) indicator variables $  \lambda_{V_i} $, and (iv) auxiliary variables $ \lambda_{v,\mathbf{u}} $. Among them, (iii) and (iv) are associated with $ \phi_\BN $ and the rest for $ \phi_{\widehat{Y}} $. For computing the maximum probability of positive prediction of the classifier, we construct  an exists-random-exists (ERE) SSAT formula with following quantifiers: we set sensitive features $ \sensitive $ with existential quantifiers in the beginning of the prefix of the SSAT formula followed by $  \lambda_{V_i}, \lambda_{v,\mathbf{u}} $, and $ X_j \in \nonsensitive \setminus \mathbf{V} $ with randomized quantifiers. The remaining variables  $ X_i \in \mathbf{V} $ are existentially quantified as their assignment is fixed by indicator variables $ \lambda_{V_i} $. In contrast, for computing the minimum probability of positive prediction of the classifier, we consider an universal-random-exists (URE) SSAT formula  where we set sensitive features $ \sensitive $ as universal quantifiers with all other quantifiers remaining same.
